Report on a Safety Checker for Petri nets

### 2013-11-18 paper/workspace/main.tex
Updated paper

bool m = true;

// Thread 1:
while (true) {
  if (m) {
    m = false
    // critical section 1
    m = true
  }
  if (m) {
    m = false
    // critical section 2
    m = true
  }
}

// Thread 2:
while (true) {
  if (m) {
    m = false
    // critical section 1
    m = true
  }
  if (m) {
    m = false
    // critical section 2
    m = true
  }
}

@@

* Petri net
\end{verbatim}

@@

  target1 >= 0
  nc      >= 0
  m       >= 0
  cs1     >= 0
  cs2     >= 0
\end{verbatim}

\begin{align*}

2 \cdot nc + m <& 2 \cdot target1 \\
  target1 \ge& 0 \\
  nc \ge& 0 \\
  m \ge& 0 \\
  cs1 \ge& target1 \\
  cs2 \ge& target1
\end{align*}

@@

For t1 construct inequation `target1 - nc - m + cs1 <= 0` in the following way.
    p - input_places + output_places <= 0
  We write `p` because the place cs1 appears in the property p and in the output places.

For t2 construct inequation `target1 - nc - m + cs2 <= 0` in the following way.
    p - input_places + output_places <= 0
  We write `p` because the place cs2 appears in the property p and in the output places.

For t3 construct inequation `- target1 + nc + m - cs1 <= 0` in the following way.
  - p - input_places + output_places <= 0
  We write `- p` because the place cs1 appears in the property p and in the input places.

For t4 construct inequation `- target1 + nc + m - cs2 <= 0` in the following way.
  - p - input_places + output_places <= 0
  We write `- p` because the place cs2 appears in the property p and in the input places.

The condition for writing `p` or `-p`:
  Write   `p` when output_places \cap vars(p) \neq \empty
  Write `- p` when input_places  \cap vars(p) \neq \empty

Output:
  target1 - nc - m + cs1   <= 0
  target1 - nc - m + cs2   <= 0
  - target1 + nc + m - cs1 <= 0
  - target1 + nc + m - cs2 <= 0

@@

  target1 >= 0
  nc      >= 0
  m       >= 0
  cs1     >= 0
  cs2     >= 0

@@

\begin{verbatim}
bool m1 = true;
bool m2 = true;

// Thread 1:
while (true) {
  if (m1 && m2) {
    m1 = false
    // critical section 1
    m1 = true
  }
  if (m1 && m2) {
    m2 = false
    // critical section 2
    m2 = true
  }
}

// Thread 2:
while (true) {
  if (m1 && m2) {
    m1 = false
    // critical section 1
    m1 = true
  }
  if (m1 && m2) {
    m2 = false
    // critical section 2
    m2 = true
  }
}

Property: The number of threads in critical sections should be at most 1
\end{verbatim}

>>>>

bool m = false;

// Thread 1:
while (true) {
  if (! test_and_set(m)) {
    // critical section 1
    m = false
  }
  if (! test_and_set(m)) {
    // critical section 2
    m = false
  }
}

// Thread 2:
while (true) {
  if (! test_and_set(m)) {
    // critical section 1
    m = false
  }
  if (! test_and_set(m)) {
    // critical section 2
    m = false
  }
}

@@

* Petri net

Place m is marked in the net exactly if m is false in the algorithm.

\end{verbatim}

@@

  target1 >= 0
  nc      >= 0
  m       >= 0
  cs1     >= target1
  cs2     >= target1
\end{verbatim}

@@

For t1 construct inequation `- nc - m + cs1 <= 0` in the following way.
   - input_places + output_places <= 0

For t2 construct inequation `- nc - m + cs2 <= 0` in the following way.
   - input_places + output_places <= 0

For t3 construct inequation `nc + m - cs1 <= 0` in the following way.
   - input_places + output_places <= 0

For t4 construct inequation `nc + m - cs2 <= 0` in the following way.
   - input_places + output_places <= 0

Output:
  - nc - m + cs1   <= 0
  - nc - m + cs2   <= 0
  + nc + m - cs1 <= 0
  + nc + m - cs2 <= 0

@@

  target1 >= 0
  nc      >= 0
  m       >= 0
  cs1     >= target1
  cs2     >= target1

@@

bool m1 = false;
bool m2 = false;

// Thread 1:
while (true) {
  if (! m2 && ! test_and_set(m1)) {
    // critical section 1
    m1 = false
  }
  if (! m1 && ! test_and_set(m2)) {
    // critical section 2
    m2 = false
  }
}

// Thread 2:
while (true) {
  if (! m2 && ! test_and_set(m1)) {
    // critical section 1
    m1 = false
  }
  if (! m1 && ! test_and_set(m2)) {
    // critical section 2
    m2 = false
  }
}

Property: The number of threads in critical sections should be at most 1

* Petri net

Place m1 is marked in the net exactly if m1 is false in the algorithm.
Place m2 is marked in the net exactly if m2 is false in the algorithm.

\end{verbatim}
